\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{
    top=0.6in,    % Set top margin
    bottom=0.6in, % Set bottom margin
    left=0.8in,   % Set left margin
    right=0.8in   % Set right margin
}
\usepackage{multicol}
\usepackage[
    colorlinks=true, % Set to true to color the links
    linkcolor=blue,  % Color for internal links
    urlcolor=blue,   % Color for external links (URLs)
    citecolor=blue,  % Color for citations
    pdfborder={0 0 1} % Adds an underline to the links
]{hyperref} % clickable hyperlinks
\pagestyle{empty}  % Disable page numbering

% Adjust line spacing for the document
\renewcommand{\baselinestretch}{0.9}

\begin{document}

% First line with name, centered and bold
\begin{center}
    {\large \textbf{Mahdy M. Karam}} \\[0.1em]  % Adjust the space between lines
    \small
    mahdykaram@outlook.com $ \cdot $ 
    \href{https://mmkaram.github.io}{Portfolio} $ \cdot $ 
    \href{https://www.linkedin.com/in/mahdykaram}{LinkedIn} $ \cdot $ 
    \href{https://github.com/mmkaram}{GitHub} $ \cdot $
    +1(425)-215-6324 $ \cdot $ Waterloo, ON
\end{center}

% Experience section
\noindent
\textbf{Experience} \\
\rule{\textwidth}{0.4pt} % Draws a line of width \textwidth and thickness 0.4pt

\textbf{PlusOne Health Expert, Cairo, Egypt (Jun 2022-Aug 2022)} - \textit{Software Engineering Intern}
\begin{itemize}
    \small % Makes the font size smaller for the list
    \setlength{\itemsep}{0pt} % Reduces space between list items
    \setlength{\parskip}{0pt} % Reduces space between paragraphs
    \item Implemented a cloud storage system using Google Healthcare for management of patient info and medical imaging files.
    \item Integrated the Google Healthcare API into the OHIF medical imaging viewer and added Arabic language support.
    \item Created a front-end system using React.js, catering to the needs of both users and medical experts.
\end{itemize}

\textbf{SigmaFit Egypt, Cairo, Egypt (Jul 2023-Aug 2023)} - \textit{Research and Development Intern}
\begin{itemize}
    \small % Makes the font size smaller for the list
    \setlength{\itemsep}{-1pt} % Reduces space between list items
    \setlength{\parskip}{0pt} % Reduces space between paragraphs
    \item Conducted research on existing tech-wear startups, discerning market viability and user acquisition.
    \item Acquired a comprehensive understanding of the mech e principles used in the development of sports analytics products.
\end{itemize}

\textbf{EPS EV, Kirkland, WA, USA (Apr 2021-Jun 2024)} - \textit{Project Manager}
\begin{itemize}
    \small % Makes the font size smaller for the list
    \setlength{\itemsep}{-1pt} % Reduces space between list items
    \setlength{\parskip}{0pt} % Reduces space between paragraphs
    \item Ordered parts and contacted EV conversion companies to begin converting a 2007 Mazda Miata into an electric vehicle.
    \item Led the Electronic Control Unit recalibration process and spearheaded the development of the infotainment system.
    \item Onboarded and delegated tasks for a team of 15 while leveraging their unique skills to achieve key milestones such as getting the car to drive on its own power in less than two years.
\end{itemize}

% Projects section
\noindent
\textbf{Projects} \\
\rule{\textwidth}{0.4pt} % Draws a line of width \textwidth and thickness 0.4pt

\textbf{Squash AI (Dec 2022-Present)}
\begin{itemize}
    \small % Makes the font size smaller for the list
    \setlength{\itemsep}{-1pt} % Reduces space between list items
    \setlength{\parskip}{0pt} % Reduces space between paragraphs
    \item Implemented advanced computer vision techniques for ball tracking in squash gameplay videos, achieving 90\% tracking accuracy on a ball with a diameter of 39.5 mm (1.56”) with a top speed of 267.151 km/h (166 mph) from 12 feet away.
    \item Contacted experts to optimize computer vision algorithms for ball and player tracking, enhancing performance.
    \item Writing Squash AI’s mobile app with Java and Swift, providing real-time feedback and performance tracking to improve players' strategies in matches and track improvement in training with a standard smartphone camera.
\end{itemize}

\textbf{Railsy (March 2024-Present)}
\begin{itemize}
    \small % Makes the font size smaller for the list
    \setlength{\itemsep}{-1pt} % Reduces space between list items
    \setlength{\parskip}{0pt} % Reduces space between paragraphs
    \item CLI tool that leverages the mail.tm API generate temporary emails and check their incoming messages.
    \item Published on the official Rust package manager index, crates.io, with 110 downloads (as of 2024/03/13).
\end{itemize}

\textbf{0K-Engine (December 2024-Present)}
\begin{itemize}
    \small % Makes the font size smaller for the list
    \setlength{\itemsep}{-1pt} % Reduces space between list items
    \setlength{\parskip}{0pt} % Reduces space between paragraphs
    \item Developing a chess engine concurrently in C++ and Rust, leveraging prebuilt chess libraries for move generation while implementing custom algorithms for optimal move selection.
    \item Utilizing optimization methods to address the intricate challenges embedded in chess engine development, showcasing the ability to efficiently tackle compute and memory-intensive problems.
\end{itemize}

\end{document}
